Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-12-10 paper/ms.tex
More work on Caryn's paper. And, responding to criticism that these messages are not helpful, I'll add blaming @bkkrueger as a way of craking out more specific text.

The single degenerate picture posits a white dwarf gaining mass
from a main-sequence companion. The process relies on a long
period of accretion combined with either steady burning or a 
series of nova explosions to allow the WD to gain
~0.6 CHECK THIS \Msun\ needed for it to approach the
limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
the Chandrasekhar limit, conditions in the compressed core are right
to ignite the thermonuclear buring that will incinerate the star.

@@

Our models are within the DDT explosion paradigm \cite{1986SvAL,
Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,fishjump2015}. 
Thermonuclear burning begins as a deflagration in the core of the WD.
The flame is unstable, and as the deflagration propagates toward the surface
of the WD, it is subject to the Rayleigh-Taylor instability that generates
turbulence and boosts buring.  
Burning proceeds as a deflagration for about one second, and then 
the flame transitions to a detonation.

@@

The mechanism by which the deflagration transistions to a detonation
is imcompletely understood, but the development of fluid instabilities
at the deflagration front, particuarly the Rayleigh-Taylor 
instability~\cite{}, is an accepted part of the process.
Many ideas have been proposed, including the deflagration front
entering a regime of distributed burning and the net
rate becoming supersonic \cite{NiemWoos97}, the unstable
flame reaching a certian fractal dimension~\cite{woosley90},
and the Zel'dovich mechanism in which condtions are right for
a pocket of fuel to 
detonate~\cite{zeldovichetal1970,KhokOranWhee97,jacketal2014}.
Our simulations assume that the transition occurs when the top of a 
rising, Rayleigh-Taylor unstable plume reaches a characteristic low
density \cite{townsley.calder.ea:flame}.

(end starter)

@@

@@

@@

Recent population synthesis work indicating a substantial contribution
to the Ia population rate from mergers where one member is a 
hybrid~\citep{yungelsonkuranov2017}.

@@

A plot of the estimated Ni56 yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
model is shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.png}
\caption{\label{fig:cumdist}
A plot of the estimated Ni56 yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
model is shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model. 
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
\caption{\label{fig:nithybrid}
Estimated Ni56 mass for Hybrid Model
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
\caption{\label{fig:nitco}
Estimated Ni56 mass for CO Model
}
\end{figure}

The figures show that the final Estimated Ni56 for the CO model is
slightly larger then the Hybrid model. Therefore, the CO produces more
Ni56. The Hybrid model has a larger range then the CO model. Also, on
average, the CO model reaches the DDT phase sooner then the Hybrid model.

This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at
the time of the DDT.

The degree of expansion was found using the time at which the first
detonation point occurred, and the mass at density less then 2e7 g/cc. The
estimated Ni56 Yield is the final estimated mass of the model.

@@

The conversion of Ni56 to Iron group elements are more pronounced in my
case. There are two assumptions as to why figure 6 is more pronounced
in my paper then in Dons.  First is that higher critical density leads
to higher electron capture resulting in less Ni56 produced. The second
is that the central ignition leads to early burning at higher density.

As the star burns mass, the surface area grows, resulting in a decrease
in density. The results show that the models that burned less mass during
the deflagration phase, expand less, produce more Ni-56. This is because
the density rich mass the model has at the DDT point is the ‘fuel’
it needs to produce Ni-56. Therefore, the more mass, the more Ni-56. On
average, the CO model, shown in figure 4, reaches the DDT faster then
the hybrid model. Figures 3 and 4 show that the hybrid model has a wider
range of estimated Ni-56 mass suggesting a greater range of burned mass
and expansion during the deflagration phase.

>>>>

The single degenerate picture posits a white dwarf gaining mass
from a main-sequence companion. The process relies on a long
period of accretion combined with either steady burning or a 
series of nova explosions to allow the WD to gain
$\sim 0.6$ CHECK THIS \Msun\ needed for it to approach the
limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
the Chandrasekhar limit, conditions in the compressed core are right
to ignite the thermonuclear buring that will incinerate the star.

@@

Our models are within the DDT explosion paradigm \cite{1986SvAL,
Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,fishjump2015}. 
In this scenario, the accretion of mass on the white dwarf compresses and 
heats the core, igniting carbon fusion and driving a period of convection
\citep{WoosWunsKuhl04,wunschwoosley2004,Kuhletal06,nonakaetal2012}.
At some point, the fusion rate becomes fast enough due to the rising
temperature that energy production exceeds convective cooling and
the deflagration phase begins in the core~\citep{Nomo84,WoosWunsKuhl04}.
This flame is unstable, and as the deflagration propagates toward the surface
of the WD, it is subject to the Rayleigh-Taylor instability that generates
turbulence and boosts buring.  
Burning proceeds as a deflagration for about one second, and then 
the flame transitions to a detonation~\citep{hoflich.khokhlov.ea:delayed}.

@@

The mechanism by which the deflagration transistions to a detonation
is imcompletely understood, but the development of fluid instabilities
at the deflagration front, particuarly the Rayleigh-Taylor 
instability~\cite{taylor+50,chandra+81}, is an accepted part of the process.
Many ideas have been proposed, including the deflagration front
entering a regime of distributed burning and the net
rate becoming supersonic \cite{NiemWoos97}, the unstable
flame reaching a certian fractal dimension~\cite{woosley90},
and the Zel'dovich mechanism in which condtions are right for
a pocket of fuel to 
detonate~\cite{zeldovichetal1970,KhokOranWhee97,jacketal2014}.
Our simulations assume that the transition occurs when the top of a 
rising, Rayleigh-Taylor unstable plume reaches a characteristic low
density \cite{townsley.calder.ea:flame}.

@@

Modern computing resources now enable simulations with unprecedented 
realism, allowing both one-dimensional simulations with a vast
amount of included physics and full three-dimensional simulations
albeit with less included physics~\cite{caldertownsley2018}.
In the area of stellar evolution, recent investigations revisiting 
late-time evolution of ????-mass stars indicate the existance of
``hybrid" white dwarfs that

@@

see however~\cite{lecoanetetal16}

@@

Also, recent population synthesis work indicating a substantial contribution
to the Ia population rate from mergers where one member is a 
hybrid~\citep{yungelsonkuranov2017}.

@@

A plot of the estimated \Ni{56} yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
model is shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.png}
\caption{\label{fig:cumdist}
A plot of the estimated \Ni{56} yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
model is shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model. 
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass for Hybrid Model
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass for CO Model
}
\end{figure}

The figures show that the final Estimated \Ni{56} for the CO model is
slightly larger then the Hybrid model. Therefore, the CO produces more
\Ni{56}. The Hybrid model has a larger range then the CO model. Also, on
average, the CO model reaches the DDT phase sooner then the Hybrid model.

This is a plot of the estimated \Ni{56} yield vs. mass below 2e7 g/cc at
the time of the DDT.

The degree of expansion was found using the time at which the first
detonation point occurred, and the mass at density less then 2e7 g/cc. The
estimated \Ni{56} Yield is the final estimated mass of the model.

@@

The conversion of \Ni{56} to Iron group elements are more pronounced in my
case. There are two assumptions as to why figure 6 is more pronounced
in my paper then in Dons.  First is that higher critical density leads
to higher electron capture resulting in less \Ni{56} produced. The second
is that the central ignition leads to early burning at higher density.

As the star burns mass, the surface area grows, resulting in a decrease
in density. The results show that the models that burned less mass during
the deflagration phase, expand less, produce more \Ni{56}. This is because
the density rich mass the model has at the DDT point is the ‘fuel’
it needs to produce \Ni{56}. Therefore, the more mass, the more Ni-56. On
average, the CO model, shown in figure 4, reaches the DDT faster then
the hybrid model. Figures 3 and 4 show that the hybrid model has a wider
range of estimated \Ni{56} mass suggesting a greater range of burned mass
and expansion during the deflagration phase.
